%\section{Proof of the Construction of Garbled Interactive Circuit}
%\label{A:sec-cons-gic}
\remove{
\begin{proof}[Proof of \cref{th:sec-cons-gic}]
  Correctness is straightforward. Let us prove simulatability.
  
  \subparagraph{Simulatability:} We need to prove the computational indistinguishability of the following two distributions:
  \begin{align*}
    \distr_0 = &\bigset{\giccir \ : \ (\iC, \vec w, \aux) \getsr \icdistr_{\secpar,
                 \icind}; \ \giccir \getsr \gicgarble(1^\secpar, \iC) }_{\secpar, \icind}\enspace, \\
    \distr_1 = &\bigset{\gicsimcir \ : \ (\iC, \vec w, \aux) \getsr \icdistr_{\secpar, \icind}; \ 
                  \gicsimcir \getsr \gicsim(1^\secpar, \trans(\iC, \nda_\secpar, \vec w)) 
                 }_{\secpar, \icind} \enspace.
  \end{align*}

  For that, we introduce $2 \nbrounds+2$ hybrid distributions $\hybrid_{0,0},\hybrid_{0,1},\hybrid_{1,0},\hybrid_{1,1},\hybrid_{2,0},\dots,\hybrid_{\nbrounds,1}$:
  \begin{description}
  \item[Hybrid $\hybrid_{\round,0}$:] This hybrid is similar to $\distr_1$, except that $\gcicaugnext^{> \round}$ and $\gckey^{> \round}$ (thus in particular $\vec \wsct^{>\round}$ is not defined) are generated as in $\distr_0$.

  We have the following straightforward claim.
  
  \begin{claim}
    $\hybrid_{0,0}$ and $\distr_{0}$ are the same distribution.
  \end{claim}
  
  \item[Hybrid $\hybrid_{\round,1}$: ]
    For $\round = 0$, this hybrid is the same as $\hybrid_{0,0}$.
    
    For $\round \ge 1$, this hybrid is similar to $\hybrid_{\round,0}$, except that:
    $\vec\wsct^{\round}$ is computed as:
    \[ \wsct^\round_k \getsr \wsenc(1^\secpar, q^\round_k, \gckey''^{\round+1}[[a^\round_k]])\enspace, \]
    where $\gckey''^{\round+1}[i,b] = \gckey[i,a^\round_{k,j}]$ for each $b \in \bits$ and each input wire $i$ corresponding to the $j$-th bit of the input $a^\round_k$ in $\icaugnext^\round$.
    In other words, for each input wire of the answers $\vec a^\round$, instead of encrypting both possible input labels with the witness selector, we encrypt twice the input label which is actually used.
    
    Thanks to consistency between the distributions $\icdistr$ and $\ndadistr$, the semantic security of the witness selector ensures that this hybrid is indistinguishable from the previous one.
    \begin{claim}
      If $\icdistr$ and $\ndadistr$ are consistent and if $\ws$ is semantically secure, then for any $\round \in [\nbrounds]$, $\hybrid_{\round,0}$ and $\hybrid_{\round,1}$ are computationally indistinguishable.
    \end{claim}

    Let $\hybrid_{\nbrounds+1,0}$ be the distribution $\distr_1$.
    As the only difference between $\hybrid_{\round,1}$ and $\hybrid_{\round+1,0}$ is that in the latter hybrid, $\gcicaugnext^{\round+1}$ and $\gckey^{\round+1}$ are simulated via $\gcsim$ instead of being generated via $\gcgarble$, we have the following claim.
    
    \begin{claim}
      If $\gc$ is simulatable, then for any $\round \in \{0,\dots,\nbrounds\}$, $\hybrid_{\round,1}$ and $\hybrid_{\round+1,0}$ are computationally indistinguishable.
    \end{claim}
  \end{description}
\end{proof}}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:
